%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\profilepic{foto}
\cvname{Oscar Ruiz\\ Cigarrillo} % Your name
\cvjobtitle{PhD. Candidate in Applied Sciences} % Job title/career

\cvdate{July 13th 1993} % Date of birth
\cvaddress{San Luis Potos\'i, M\'exico} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{+52 4442384382} % Phone number
\cvsite{https://github.com/RUCO13} % Personal website
\cvsited{https://wakatime.com/@RUCO13} % Personal website
\cvmail{ruizoscar.1393@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 ABOUT ME
%----------------------------------------------------------------------------------------

\aboutme{} % To have no About Me section, just remove all the text and leave \aboutme{}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{{MATLAB/6},{Mathematica/6},{C/5},{Julia/5},{C++/5},{\LaTeX/6},{Fortran/6},{Python/6},{DFT packages/5},{Linux, MacOs, Windows/6}}

\lang{{Spanish/6},{English/5}}

%------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6
%\skillstext{{lovely/4},{narcissistic/3}}

%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar



\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2017-2021}{PhD candidate in Applied Science (Photonics)}
	                       {\\Universidad Aut\'onoma de San Luis Potos\'i, M\'exico}
	                       {\emph{``Optical anisotropy study in coupled quantum wells, a novel source of undisturbed systems''}}
	\twentyitem{2015-2017}{Master degree in Applied Science (Photonics)}
	                      {\\Universidad Aut\'onoma de San Luis Potos\'i, M\'exico}
	                      {\emph{``Growth and Characterization of Semiconductor Optical \\ Microcavities''}}
	\twentyitem{2011-2015}{Bachelor degree in physics engineering}
	                      {\\Universidad Aut\'onoma de San Luis Potos\'i, M\'exico}
	                      {Grade: 9.2/10}
	
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}



%----------------------------------------------------------------------------------------
%	 PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitemshort{2017}{{\color{blue}``Optical detection of graphene nanoribbons synthesized on stepped SiC surfaces''}\\
	                        L.F. Lastras-Mart{\'\i}nez, J. Almendarez-Rodr{\'\i}guez, G. Flores-Rangel, N.A. Ulloa-Castillo, {\color{black} O. Ruiz-Cigarrillo}, C.A. Ibarra-Becerra , R. Castro-Garc{\'\i}a, R.E. Balderas-Navarro, M.H. Oliveira Jr and  J.M.J Lopes, \textit{Journal of Applied Physics} \textbf{122(3)},  035701, (2017)}


   	\twentyitemshort{2017}{{\color{blue}``Microscopic optical anisotropy of exciton-polaritons in a GaAs-based semiconductor microcavity''}\\
   	L.F. Lastras-Mart{\'\i}nez, E. Cerda-M\'endez, N.A. Ulloa-Castillo,R. Herrera-Jasso, L. E. Rodríguez-Tapia, {\color{black} O. Ruiz-Cigarrillo}, R. Castro-Garc\'ia, K. Biermann, P. V. Santos. \textit{Physical Review B},\textbf{ 2017, vol. 96, no 23, p. 235306}}
   
   	\twentyitemshort{2019}{{\color{blue}``Differential reflectance contrast technique in near field limit: Application to graphene''}\\
   	 L.F. Lastras-Mart{\'\i}nez, D. Medina-Escobedo, G. Flores-Rangel, R.E. Balderas-Navarro, {\color{black} O. Ruiz-Cigarrillo}, R. Castro-Garc{\'\i}a,
   	 M. del P. Morales-Morelos, J. Ortega-Gallegos, M. Losurdo. \textit{ AIP Advances},\textbf{ 2019, vol. 9, no 4, p. 045309}}
    
    \twentyitemshort{2021}{{\color{blue}``Optical contrast in the near-field limit for structural characterization of graphene nanoribbons''}\\
    	 G. Flores-Rangel, L.F. Lastras-Mart{\'\i}nez, R. Castro-Garc{\'\i}a, {\color{black} O. Ruiz-Cigarrillo}, R.E. Balderas-Navarro, L.D.Espinosa-Cuellar A.Lastras-Martínez, J.M.J.Lopes. \textit{ AIP Advances},\textbf{ Volume 536, 15 January 2021, 147710}}
     
    \twentyitemshort{2021}{{\color{blue}``Optical anisotropies of asymmetric double GaAs (001) quantum wells''}\\
     {\color{black}O. Ruiz-Cigarrillo}, L. F. Lastras-Mart\'{\i}nez, E. A.
     Cerda-M\'endez, et al. \textit{Physical Review B},\textbf{ 2021, vol. 103, no 3, p. 035309.}}
	 \twentyitemshort{2022}{{\color{blue}`Photoluminescence of double quantum wells: asymmetry and excitation laser wavelength effects''}\\
	 C. A. Bravo-Velázquez,L. F. Lastras-Mart\'{\i}nez{\color{black}O. Ruiz-Cigarrillo}, et al. \textit{physica status solidi (b)},\textbf{  2022, vol. 259, issue 4.}}
   
	%\twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}

\section{Awards}

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitemshort{2017}{Third place, Research level in the poster competition Teaching and Research 2017 "Fis. Candelario Pérez Rosales", XVII Week}
	\twentyitemshort{2018}{Third place, Research level in the poster competition Teaching and Research 2018 "Fis. Candelario Perez Rosales", XVIII Semana.}
	%\twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}
\newpage 
\makeprofile 
%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2017}{Complex Variable, Electromagnetism}
	{\\UASLP}
	{Assistant Professor}
	
	\twentyitem{2017}{Creating and Editing Scientific Documents in LaTeX: Basic Course
		Complex Variable, Electromagnetism}
	{UASLP}
	{Course}
	
	\twentyitem{2017}{Physics}
	{\\Secondary level}
	{Professor}
	
	\twentyitem{2019-present}{Calculus (Difference and Integral), Physics I, Physics II, Probability and Statistics, Mathematics I (Algebra), Mathematics III (Analytic Geometry) }
	{\\High School level}
	{Professor}
	
	\twentyitem{2019-present}{Programming,Numerical Methods, Operating Systems, Calculus (Differential  and Integral), Physics I, Physics II, Probability and Statistics, Advanced Algebra}
	{\\University level}
	 {Professor}
	
\end{twenty}



\section{Participation National Conferences}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2016}{National Physics Congress}
	                 {\\Growth and Characterization of Optical Microcavities of (Al,Ga)As.}
                     {Poster}
                     
   	\twentyitem{2017}{X Annual Meeting of the Quantum Information Division}
   {\\ Advances in III-V microcavity growth for solid-state quantum condensates}
   {Poster}
  

\end{twenty}



\begin{twenty}
	  	\twentyitem{2017}{National Physics Congress}
	{\\ In-situ and real-time optical growth and characterization of (Al,Ga)As microcavities.
		National Physics Congress
	}
	{Talk}
	
\twentyitem{2018}{Solid State Division Annual Meeting}
	{\\ Detection of Indirect Excitons in Coupled Quantum Wells Using Photoreflectance}
	{Talk}
	
\twentyitem{2019}{Solid State Division Annual Meeting}
	{\\Study of Indirect Excitons and Trions in coupled asymmetric quantum wells}
	{Poster}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}



\section{Interests}
\\\\
My main interest is learning physics. In my PhD project I focused on the development of experimental solid state physics specifically in the field of optical spectroscopy and decided to take it in hand with computational physics, developing my own codes and learning from existing codes. I consider numerical calculations in experimental physics are a powerful tool to understand the complexity in solid state and condensed matter physics. I consider myself an enthusiast of open-source code and software, and I am very committed to teaching my knowledge about it.

\end{document} 